---
title: "Homework #1 -- Pet Names Dataset"
author: "Ryam Radi M "
date: "`r Sys.Date()`"
output: github_document
---

**Student ID: 2201001476 **

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1.how many pets are included in this dataset ?


(4 points)
```{r}

```
>52. 519



`2.how many variables do we have for each pet ?

(4 points)

```{r}

```
>variables: 7


`3. Copy the code provided in the homework documentation and paste it here . 

# A tibble: 13,930 x 2
   animal_name     n
   <chr>       <int>
 1 NA            483
 2 Lucy          439
 3 Charlie       387
 4 Luna          355
 5 Bella         331
 6 Max           270
 7 Daisy         261
 8 Molly         240
 9 Jack          232
10 Lily          232
# .. with 13,920 more rows

# A tibble: 16,823 x 3
# Groups:   species [4]
   species animal_name     n
   <chr>   <chr>       <int>
 1 Cat     NA            406
 2 Dog     Lucy          337
 3 Dog     Charlie       306
 4 Dog     Bella         249
 5 Dog     Luna          244
 6 Dog     Daisy         221
 7 Dog     Cooper        189
 8 Dog     Lola          187
 9 Dog     Max           186
10 Dog     Molly         186
# … with 16,813 more rows

# A tibble: 4 x 2
  species     n
  <chr>   <int>
1 Dog     35181
2 Cat     17294
3 Goat       38
4 Pig         6

(4 points)

```{r}

```
Write your narrative here



`4..
# A tibble: 53 x 3
# Groups:   species [4]
   species animal_name     n
   <chr>   <chr>       <int>
 1 Cat     NA            406
 2 Cat     Luna          111
 3 Cat     Lucy          102
 4 Cat     Lily           86
 5 Cat     Max            83
 6 Dog     Lucy          337
 7 Dog     Charlie       306
 8 Dog     Bella         249
 9 Dog     Luna          244
10 Dog     Daisy         221
# … with 43 more rows

(10 points)

```{r species-name-top5, eval=TRUE}

```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Oliver and lily

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Answer here

(4 points)